Characterization of foreign direct investment in Mozambique and implications

### 2015-09-24 paper.Rmd
double columns!

---
title: Characterization of foreign direct investment in Mozambique and implications
  for public health
author: "Joe Brew and Elisa Sicuri"
csl: health-economics-policy-and-law.csl
output:
  pdf_document:
    includes:
      in_header: style.sty
  html_document: default
highlight: zenburn
latex_engine: xelatex
header-includes: \usepackage{longtable}
bibliography: ../fdi_moz.bib
---

@@

## Introduction 
Mozabique's recent economic growth has been facilitated by the government's open policy towards foreign investment, a plentiful supply of natural resources (particularly minerals and hydrocarbons) [@Rogers] and relatively inexpensive labor. Improvements in health have accompanied economic expansion, but Mozambique still lags behind in basic health outcomes - particularly those related to malaria - even by regional standards[@whostat]. Though strong evidence shows that improved health yields substantial economic benefits [@World1999, @Bloom2008], private foreign investment has played only a secondary role in malaria prevention and control in recent years.

@@

>>>>

---
title: Characterization of foreign direct investment in Mozambique and implications
  for public health
author: "Joe Brew and Elisa Sicuri"
csl: health-economics-policy-and-law.csl
output:
  pdf_document:
    includes:
      in_header: style.sty
  html_document: default
highlight: zenburn
latex_engine: xelatex
bibliography: ../fdi_moz.bib
---

@@

## Introduction

\columnsbegin

Mozabique's recent economic growth has been facilitated by the government's open policy towards foreign investment, a plentiful supply of natural resources (particularly minerals and hydrocarbons) [@Rogers] and relatively inexpensive labor. Improvements in health have accompanied economic expansion, but Mozambique still lags behind in basic health outcomes - particularly those related to malaria - even by regional standards[@whostat]. Though strong evidence shows that improved health yields substantial economic benefits [@World1999, @Bloom2008], private foreign investment has played only a secondary role in malaria prevention and control in recent years.

@@

\columnsend
